Adopting agile in the large: motivations, success factors and challenges

### 2014-04-24 journal/article.tex
Reasons to change: management problems

>>>>

A common problem that was acknowledged in organizations was overhead in process,
which showed as bureucracy and needless costs. Examples on overhead in process
were unproductive meetings [P38], sign-offs and gates [P9], excessive focus on
conformance to process [P40], and change management overhead [P51]. Creating
excessive documentation instead of business value was seen as a problem in some
cases [P24, P35].
From business representatives point of view the processes were unreasonably
costly, while at the same time insufficiently capable of delivering business
value [P36, P46, P49]. In one case business realized that customers did not
request the heavy CMMI based process [P24].
A heavy process resulted often in ignoring the process, only paying ``lip
service'' to the process, or applying its steps retroactively [P6, P9, P49].
Seffernick described how applying the waterfall process had teams ``still
developing the same old way but slower because of the additional process''
[P46].
